An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-03-04 poly-embed-journal/poly-embed-journal.tex

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
\jessie{
	\begin{itemize}
		\item Add figures of Bayes risks of 0-1, logistic, and hinge losses (Jessie: Have made them, not sure where would be the best place to insert them/if you think this would be helpful)
		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
		\item Replace Proposition 2 with Lemma 7?
		\item Theorem 2: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
		\item Links: cool to point out that when L is polyhedral, \prop{L} has a finite range (this result) and so does its (multivalued map) inverse (trim result)
		\item Links: sketch vs full proof
		\item Commentary on how any loss embedding ell must be polyhedral ish
	\end{itemize}}

@@

@@

\begin{proposition}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
    \end{enumerate}
    %\raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}\jessie{Consolidated; original below.}
	Let $L$ elicit $\Gamma$.

	1 $\Rightarrow$ 2:
        %\jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
  If $\Gamma$ embeds a finite $\gamma$, then Lemma~\ref{lem:embed-defs-equiv} says there is be a discrete loss $\ell$ embedded by $L$ such that $\ell$ elicits $\gamma$.
  \raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma. \jessie{Is this better?}}
  By Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$.
%  \raft{Replace with ``As $\R$ is finite, we conclude $\trim(\Gamma)$ is finite.'' or similar}
  As $\R$ is finite, we conclude that $\trim(\Gamma)$ is also finite.
%  Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
  \raft{Why is it nonempty though?  \jessie{Just above definition 2, we specify that properties are nonempty}}
  Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \emptyset$), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.

@@

	1 $\Rightarrow$ 3: 
	Let $\varphi: \R \to \reals^d$ by the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
	The latter set is equal to $\{\gamma_r : r \in \R\}$ by $\Gamma$ embedding $\gamma$.
	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the simplex.
	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.
%	\hrule
%	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
%	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
%	As the risks are equal, this is also true for $\Gamma$.
%	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
%	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
%	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
%	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.

@@

\end{proof}

\jessiet{Can we remove this?}
\begin{proof}[Original]
	Let $L$ elicit $\Gamma$.

@@

\subsection{Refining properties} \btw{JESSIE: This needs more narrative text.  I also don't know if this should go in the Appendix, given it doesn't really connect to the rest of the paper, though I think the point it makes (surrogates work for nearly any indirectly elicited property) is worth having in the body.}

@@

	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a link from $\gamma'$ to $\gamma$:
	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))} = \gamma_{\psi'(r')}$.
	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
\end{proof}

\jessie{I am going to suggest cutting this; I don't think it adds much to the narrative and forward refs results from calibrated links.}
\begin{corollary}\label{cor:ie-sufficient} \jessiet{Added 7.24.20.  Probably too long to be a Corollary proof, but would rather start too long than too short.  Also the proof has a forward ref}
	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then for any loss $\ell'$ eliciting $\gamma'$, there exists a link $\bar \psi$ such that $(L, \bar \psi)$ is calibrated with respect to $\ell'$.
\end{corollary}
\begin{proof}
	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a property $\gamma\simplex \toto \R$ which refines $\gamma'$.
	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$. \jessie{Relies on results in the next section...}
	Moreover, as $\gamma$ refines $\gamma'$, take any link $\psi': r \mapsto r'$, where $\gamma_r \subseteq \gamma'_{r'}$. 
	(We know such a link exists by refinement.)
	Consider $\tilde \psi := \psi \circ \psi'$.

	Now, we show that $(L, \tilde \psi)$ is calibrated with respect to $\ell'$.
	Consider that since $\Gamma$ embeds $\gamma$, we have a link $\bar \psi$ such that $(L,\bar \psi)$ is calibrated with respect to $\ell$ eliciting $\gamma$.
	It then suffices to show
	\begin{align*}
	\inf_{u}\inprod{p}{L(u)} &< \inf_{u : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)}\\
	&\leq \inf_{u : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L(u)}~.~
	\end{align*}
	This first statement is true as embedding implies calibration (Theorem~\ref{thm:eps-thick-calibrated}), and the second is true if $\{u : \psi'(u) \not \in \gamma'(p) \} \subseteq \{u : \psi(u) \not \in \gamma(p) \}$; we show the contrapositive.
	Take $u \in \reals^d$ so that $\psi(u) \in \gamma(p)$.
	\begin{align*}
	\psi(u) \in \gamma(p) &\iff \psi' \circ \psi(u) \in \psi' \circ \gamma(p)\\
	&\iff \tilde \psi(u) \in \gamma'(p)~,~
	\end{align*}
	where the last inequality follows by construction of $\psi'$.
\end{proof}

@@

@@

Note that the given \emph{Cascade Surrogate} of~\cite[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\cite{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.

>>>>

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\OP}{\mathcal{OP}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
\jessie{
	\begin{itemize}
		\item Add figures of Bayes risks of 0-1, logistic, and hinge losses (Jessie: Have made them, not sure where would be the best place to insert them/if you think this would be helpful)
		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
		\item Replace Proposition 2 with Lemma 7?
		\item Theorem 2: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
		\item Links: cool to point out that when L is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)
		\item Links: sketch vs full proof
		\item Commentary on how any loss embedding ell must be polyhedral ish
	\end{itemize}}

@@

In Proposition~\ref{prop:embed-bayes-risks}, we show an equivalent condition to embedding, whose proof relies on the following Lemma about the Bayes Risk of a ``restricted'' surrogate.
\begin{lemma}\label{lem:loss-restrict}
	Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
	Then $L|_{\R_2}$ ($L$ restricted to $\R_2$) elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
	Moreover, the Bayes risks of $L$ and $L|_{\R_2}$ are the same.
\end{lemma}
\begin{proof}
	Let $p\in\simplex$ be fixed throughout.
	First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
	Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
	For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
	By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
	On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
	On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
	But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
	We now see $r \in \Gamma(p) \cap \R_2$.
	Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
\end{proof}

@@

\begin{proposition}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
    \end{enumerate}
    %\raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}
	Let $L$ elicit $\Gamma$.

	1 $\Rightarrow$ 2:
        %\jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
  If $\Gamma$ embeds a finite $\gamma$, then Lemma~\ref{lem:embed-defs-equiv} says there is a discrete loss $\ell$ embedded by $L$ such that $\ell$ elicits $\gamma$.
  \raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma. \jessie{Is this better?}}
  By Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$.
%  \raft{Replace with ``As $\R$ is finite, we conclude $\trim(\Gamma)$ is finite.'' or similar}
  As $\R$ is finite, we conclude that $\trim(\Gamma)$ is also finite.
%  Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
  \raft{Why is it nonempty though?  \jessie{Just above definition 2, we specify that properties are nonempty}}
  Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \{\emptyset\}$), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.

@@

	1 $\Rightarrow$ 3: 
	Let $\varphi: \R \to \reals^d$ be the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
	The latter set is equal to $\{\gamma_r : r \in \R\}$ by Lemma~\ref{lem:embedded-level-sets-trim}.
	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the simplex.
	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.
%	\hrule
%	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
%	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
%	As the risks are equal, this is also true for $\Gamma$.
%	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
%	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
%	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
%	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.

@@

\end{proof}
\jessiet{03.01.21 - Old version moved to comment}
%\jessiet{Can we remove this?}
%\begin{proof}[Original]
%	Let $L$ elicit $\Gamma$.
%	
%	1 $\Rightarrow$ 2:
%	By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
%	Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
%	By the Lemma, we also have $G = G_\R$.
%	As $\gamma$ is finite, $G$ is polyhedral.
%	Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
%	(See Theorem~\ref{thm:aurenhammer}.)
%	As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
%	This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
%	Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
%	We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
%	Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
%	
%	2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
%	Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
%	We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
%	The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
%	Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
%	Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
%	
%	3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
%	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
%	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
%	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
%\end{proof}

@@

\btw{JESSIE: This needs more narrative text.  I also don't know if this should go in the Appendix, given it doesn't really connect to the rest of the paper, though I think the point it makes (surrogates work for nearly any indirectly elicited property) is worth having in the body.}

@@

	%\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a link from $\gamma'$ to $\gamma$:
	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))} = \gamma_{\psi'(r')}$.
	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
\end{proof}

\begin{theorem}\label{cor:ie-sufficient}
	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then for any loss $\ell'$ eliciting $\gamma'$, there exists a link $\bar \psi$ such that $(L, \bar \psi)$ is calibrated, and therefore consistent, with respect to $\ell'$.
\end{theorem}
\begin{proof}
	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a property $\gamma:\simplex \toto \R$ which refines $\gamma'$.
	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$. \jessie{Relies on results in the next section...}
	Moreover, as $\gamma$ refines $\gamma'$, take any link $\psi': r \mapsto r'$, where $\gamma_r \subseteq \gamma'_{r'}$. 
	(We know such a link exists by refinement.)
	Consider $\tilde \psi := \psi \circ \psi'$.

	Now, we show that $(L, \tilde \psi)$ is calibrated with respect to $\ell'$.
	Consider that since $\Gamma$ embeds $\gamma$, we have a link $\bar \psi$ such that $(L,\bar \psi)$ is calibrated with respect to $\ell$ eliciting $\gamma$.
	It then suffices to show
	\begin{align*}
	\inf_{u}\inprod{p}{L(u)} &< \inf_{u : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)}\\
	&\leq \inf_{u : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L(u)}~.~
	\end{align*}
	This first statement is true as embedding implies calibration (Theorem~\ref{thm:eps-thick-calibrated}), and the second is true if $\{u : \psi'(u) \not \in \gamma'(p) \} \subseteq \{u : \psi(u) \not \in \gamma(p) \}$; we show the contrapositive.
	Take $u \in \reals^d$ so that $\psi(u) \in \gamma(p)$.
	\begin{align*}
	\psi(u) \in \gamma(p) &\iff \psi' \circ \psi(u) \in \psi' \circ \gamma(p)\\
	&\iff \tilde \psi(u) \in \gamma'(p)~,~
	\end{align*}
	where the last inequality follows by construction of $\psi'$.
	Consistency now follows as calibration and consistency are equivalent in this setting.
\end{proof}

@@

\btw{New (March 2 2021): adding Yutong's paper}
\subsection{Embedding Ordered Partitions}
\citet*{wang2020weston} use the embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.

An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, S_l) \in \OP_n$ by
\begin{align*}
\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
\end{align*}
The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
\btw{TODO: Add simplex diagrams for this!}

@@

Note that the given \emph{Cascade Surrogate} of~\citet[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\citet{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
